Deep Learning

### 2015-02-17 deepreview.tex
improved convnet caption

\begin{figure}
\begin{center}
  \vspace{0.2cm}
  \includegraphics[width=0.70\linewidth]{convnet-diagram}
\end{center}
\vspace{-0.6cm}
\caption{The outputs of each layer of a typical convolutional network architecture
applied on the image of a handwritten digit (on the top left). Each rectangular
image corresponds to one of the features, detected at each of the image positions.
Each column corresponds to a layer, with information flowing from the left to
the right.
}
%\vspace{-0.8cm}
\label{fig:convnet}
\end{figure}

>>>>

\begin{figure}
\begin{center}
  \vspace{0.2cm}
  \includegraphics[width=0.70\linewidth]{convnet-diagram}
\end{center}
\vspace{-0.6cm}
\caption{The outputs of each layer (column) and feature map (rectangular image)
of a typical convolutional network architecture
applied on the image of a handwritten digit (on the top left). Each rectangular
image is a feature map, corresponding to one of the learned features 
detected at each of the image positions.
Each column corresponds to a layer, with information flowing from the left to
the right. We see that lower level features mostly act as oriented edge detectors.
}
%\vspace{-0.8cm}
\label{fig:convnet}
\end{figure}
